Supplement

### 2023-02-16 06_Paper/ER-ED/ERED_Stage2/Supplement.Rmd
added placement

papaja::apa_table(
  df.NV.subj,
  caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
  escape = FALSE)

papaja::apa_table(
  df.NV.EMG,
  caption = "Results of Shapiro-Wilk test for normal distribution of *Corrugator* and *Levator* activity for all strategies.",
  escape = FALSE)

>>>>

papaja::apa_table(
  df.NV.subj,
  caption = "Results of Shapiro-Wilk test for normal distribution of subjective arousal and effort ratings for all strategies.",
  escape = FALSE,
  placement = "H")

papaja::apa_table(
  df.NV.EMG,
  caption = "Results of Shapiro-Wilk test for normal distribution of Corrugator and Levator activity for all strategies.",
  escape = FALSE,
  placement = "H")
